An assessment of the biodiversity - ecosystem function relationship in southern African woodlands

### 2019-11-15 manuscript/include/struc_model_fit_clust_stats.tex
More functions in SEM to automate clusters
Updated figures and text, pre-comments from Kyle
Made tikz path diagrams
Updated flow chart of data cleaning

% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
% Date and time: Tue, Oct 22, 2019 - 11:39:36
\begin{table}[!htbp] \centering 
  \caption{} 
  \label{struc_model_fit_clust_stats} 
\begin{tabular}{@{\extracolsep{5pt}} cccccccccccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & npar & chisq & df & cfi & tli & logl & aic & bic & ntotal & rmsea & rmsea.ci.lower & rmsea.ci.upper & srmr \\ 
\hline \\[-1.8ex] 
C1 & $12$ & $4.660$ & $3$ & $0.997$ & $0.989$ & $$-$1854$ & $3732$ & $3777.900$ & $337$ & $0.040$ & $0$ & $0.108$ & $0.016$ \\ 
C2 & $12$ & $22.830$ & $3$ & $0.982$ & $0.939$ & $$-$2838.600$ & $5701.200$ & $5754.300$ & $619$ & $0.100$ & $0.066$ & $0.145$ & $0.017$ \\ 
C3 & $12$ & $7.910$ & $3$ & $0.961$ & $0.871$ & $$-$502.300$ & $1028.500$ & $1057$ & $79$ & $0.140$ & $0.012$ & $0.270$ & $0.073$ \\ 
C4 & $12$ & $1.690$ & $3$ & $1$ & $1.054$ & $$-$139.600$ & $303.100$ & $318.200$ & $26$ & $0$ & $0$ & $0.265$ & $0.048$ \\ 
C5 & $12$ & $1.120$ & $3$ & $1$ & $1.068$ & $$-$368.200$ & $760.400$ & $785.300$ & $59$ & $0$ & $0$ & $0.146$ & $0.034$ \\ 
\hline \\[-1.8ex] 
\end{tabular} 
\end{table}

>>>>

% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
% Date and time: Fri, Nov 08, 2019 - 17:15:20
\begin{table}[!htbp] \centering 
  \caption{Model fit statistics for SEMs investigating the effects of tree diversity and stem density on AGB (\autoref{struc_mod}).} 
  \label{struc_model_fit_clust_stats} 
\begin{tabular}{@{\extracolsep{0pt}} ccccccccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
{Cluster} & {Params.} & {n} & {$\chi^{2}$} & {DoF} & {CFI} & {TLI} & {LogLik} & {AIC} & {RMSEA} & {SRMR} \\
\hline \\[-1.8ex] 
C1 & 12 & 420 & 10.430 & 3 & 0.987 & 0.958 & -2630.700 & 5285.300 & 0.080 & 0.029 \\ 
C2 & 12 & 671 & 50.320 & 3 & 0.942 & 0.806 & -3730.200 & 7484.300 & 0.150 & 0.052 \\ 
C3 & 12 & 105 & 24.970 & 3 & 0.880 & 0.601 & -619.100 & 1262.300 & 0.260 & 0.142 \\ 
C4 & 12 & 46 & 2.710 & 3 & 1 & 1.008 & -257.900 & 539.900 & 0 & 0.025 \\ 
C5 & 12 & 84 & 5.400 & 3 & 0.981 & 0.936 & -529.500 & 1083 & 0.100 & 0.085 \\ 
All & 12 & 1326 & 62.210 & 3 & 0.968 & 0.895 & -8110.500 & 16245 & 0.120 & 0.036 \\ 
\hline \\[-1.8ex] 
\end{tabular} 
\end{table}
